\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{0pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Anarv Singh} \\[2mm]
    \footnotesize \raisebox{-0.1\height}
    \faMapMarker\ \underline{Chicago, IL} ~
    \faMobile\ \underline{+1 (312)371-1745} ~
    {\faEnvelope\ \underline{anarvsingh@gmail.com}} ~
    {\faLinkedin\ \underline{\href{https://www.linkedin.com/in/anarv-s-91811a173/}{LinkedIn}}} ~
    {\faGithub\ \underline{\href{https://github.com/Anarvsingh}{GitHub}}} ~
    }
    
    \vspace{-15pt}
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education} \\[1mm]
\resumeSubHeadingListStart 
  \resumeSubheading
    {Illinois Institute of Technology}{ May 2025}
    {Master’s In Computer Science}{Chicago, USA}
\resumeSubHeadingListEnd
\vspace{-10pt}
\resumeItemListStart
  \resumeItem {Awarded Graduate Pathway Scholarship for academic excellence}
  \vspace{-9pt}
  \resumeItem {Courses: Operating Systems, Algorithms and Data Structures, Database Organization, Advanced Database Organization, Software Project Management, Data Communications}
\resumeItemListEnd

\resumeSubHeadingListStart
\vspace{-10pt}
  \resumeSubheading
    {SRM Institute of Science and Technology}{May 2020}
    {Bachelor of Computer Engineering}{Chennai, India}
\resumeSubHeadingListEnd
\vspace{-10pt}
\resumeItemListStart
  \resumeItem {Courses: Computer Networks, Operating Systems, Computer Architecture, Java Programming, Algorithms and Data Structures}
\resumeItemListEnd
\vspace{-15pt}

%-----------WORK EXPERIENCE---------------
\section{Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Conga}{Aug 2022 – July 2023}{Associate Developer}{India} 
  \resumeItemListStart
    \resumeItem{Developed real-time claim status updates using Spring Boot and Java, enhancing transparency and client satisfaction.}
  \resumeItem{Worked on REST APIs and developed business features with Spring Boot, improving system functionality.}
    \resumeItem{Integrated Redis cache with Spring Boot for efficient data caching, significantly boosting application performance and reducing database load.}
    \resumeItem{Participated in Agile sprints and code reviews with cross-functional teams, integrating REST APIs and React.js to support scalable, high-performance solutions.}
  \resumeItemListEnd

  \vspace{-7pt}
  \resumeSubheading{HCL Tech}{Dec 2020 – July 2022}{Analyst}{India} 
  \resumeItemListStart
      \resumeItem{Worked on the implementation of live tracking system using Kafka, enhancing decision-making speed.}
    \resumeItem{Built real-time integrations with SpringBoot and REST APIs, optimizing data flows with PostgreSQL for reliability and scalability in a CI/CD pipeline.}
    \resumeItem{Performed root cause analysis with Splunk and SLF4J, enhancing system performance and collaborating on test plans with a 4-person Agile team.}
    \resumeItem{Written Unit test cases to ensure code quality and reliability across all implemented features.}
    \resumeItem{Contributed to the design and development of the microservices architecture, enabling easy deployment and maintenance.}
  \resumeItemListEnd
\vspace{-12pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects} 
\vspace{-9pt}
\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{HelpBot} $|$ \href{https://github.com/Anarvsingh/HelpBot}{\underline{View Project}}}
  {React.js $|$ TypeScript $|$ Node.js $|$ AWS}
  \\[5mm]
\resumeItemListStart
  \resumeItem{Developed a real-time AI chatbot with React.js and Node.js, integrating LangChain on AWS for scalable, low-latency responses in a distributed system.}
  \resumeItem{Optimized performance with TypeScript and Convex, participating in iterative design reviews to ensure fault-tolerant, production-ready features.}
  \resumeItem{Collaborated on architecture and test automation, delivering resilient solutions with reusable React.js components in an Agile workflow.}
\resumeItemListEnd

\vspace{-12pt}
\resumeProjectHeading
  {\textbf{SkillCheck} $|$ \href{https://github.com/Anarvsingh/SkillCheck2}{\underline{View Project}}}
  {React.js $|$ TypeScript $|$ Node.js $|$ Docker}
  \\[5mm]
\resumeItemListStart
  \resumeItem{Built a distributed platform with React.js microservices and Node.js, supporting \textbf{200+} users with real-time video features on AWS.}
  \resumeItem{Implemented CI/CD with Docker, achieving sub-2-second performance via optimized algorithms, ensuring scalability and reliability.}
  \resumeItem{Led integration of 4+ services, collaborating on test plans and code reviews to deliver robust, fault-tolerant solutions in a fast-paced setting.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{   
    \textbf{Languages}: Java, SQL, JavaScript, Python, TypeScript, HTML5, CSS,  \\[1mm]
    \textbf{Developer Tools}: AWS, Git, Splunk, Prometheus, Linux, Docker, Postman, Jira \\[1mm]
    \textbf{Libraries/Frameworks}: Spring Boot, Node.js, PostgreSQL, REST API, React.js, Next.js, Tailwind CSS, Convex, Kafka \\[1mm]
  }}
\end{itemize}
\vspace{-16pt}
\vspace{3pt}
\vspace{10pt}

\vspace{-15pt}

\end{document}
